When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2017-11-10 paper/paper.tex
More notation

Suppose our labels are drawn randomly from a set $L = \{ 1, \ldots, k \}$, where $k$ is reasonably
small compared to the number of pattern vertices $p$. Recall that $\ell(v)$ is the label of vertex
$v$. By defining \[ \operatorname{V}(P)\vert_n = \{ v \in \operatorname{V}(P) : \ell(v) = x \} \] to
be the set of vertices with label $x$, we can partition the pattern vertices by label into disjoint
sets $\{\operatorname{V}(P)\vert_1, \ldots, \operatorname{V}(P)\vert_k \}\textnormal{\,,}$ each of
which is expected to contain $\nicefrac{p}{k}$ vertices. Similarly, we may partition the target
vertices into disjoint sets $\{ \operatorname{V}(T)\vert_1, \ldots, \operatorname{V}(T)\vert_k \}$.

>>>>

Suppose our labels are drawn randomly from a set $L = \{ 1, \ldots, k \}$, where $k$ is reasonably
small compared to the number of pattern vertices $p$. Recall that $\ell(v)$ is the label of vertex
$v$. By defining \[ \operatorname{V}(P)\vert_x = \{ v \in \operatorname{V}(P) : \ell(v) = x \} \] to
be the set of vertices with label $x$, we can partition the pattern vertices by label into disjoint
sets $\{\operatorname{V}(P)\vert_1, \ldots, \operatorname{V}(P)\vert_k \}\textnormal{\,,}$ each of
which is expected to contain $\nicefrac{p}{k}$ vertices. Similarly, we may partition the target
vertices into disjoint sets $\{ \operatorname{V}(T)\vert_1, \ldots, \operatorname{V}(T)\vert_k \}$.
